DP Problems of Interest

### 2012-10-01 docs/roadmap/problems.tex
Stub plan.

% ------------------------------------------------------------------------------------------------
\newpage
\subsection{Zuker folding}\ol
\item Problem: folding a RNA string $S$ over itself $\left\lfloor |S| / 2 \right\rfloor = n$.
\item Matrices: $M_{n\times n}, V_{n\times n}, B_{n \times n}, {\color{red} F???}$
\item Alphabets:\ul
	\item Input: $\Sigma(S)=\{A,C,G,U\}$.
	\item Cost matrix: $\Sigma(W)=\Sigma(V)=\Sigma(F)=\{0..n\}$
	\item Backtrack matrix: $\Sigma(B)=\{stop, {\color{red} S,W, XXX here} \}$
	\ule
{\color{red}
\item Initialization:\ul
	\item Cost matrices:\ul
		\item XXX: $W$,$V$
		\item $F_{(0)}=0$
	\ule
	\item Backtrack matrix: $B$
	\ule

@@

>>>>

% ----------------------------------------------
\newpage
\subsection{Zuker folding}\ol
\item Problem: folding a RNA string $S$ over itself $\left\lfloor |S| / 2 \right\rfloor = n$.
\item Matrices: $M_{n\times n}, V_{n\times n}, B_{n \times n}, {\color{red} F???}$
\item Alphabets:\ul
	\item Input: $\Sigma(S)=\{A,C,G,U\}$.
	\item Cost matrix: $\Sigma(W)=\Sigma(V)=\Sigma(F)=\{0..n\}$
	\item Backtrack matrix: $\Sigma(B)=\{stop, {\color{red} S,W, XXX here} \}$
	\ule
{\color{red}
\item Initialization:\ul
	\item Cost matrices:\ul
		\item XXX: $W$,$V$
		\item $F_{(0)}=0$
	\ule
	\item Backtrack matrix: $B$
	\ule

@@

% ------------------------------------------------------------------------------------------------
\newpage
\section{Plan} \ol
\item Define/agree some problems to take into consideration, agree on them
\item Concerns separation: common architecture enables flexibility (exchange components) \ul
	\item Block processor: CPU, GPU, FPGA, must allow variation of width and height
	\item Memory stats computation (min, sum, ... column/line combinations): CPU, GPU
	\item Scheduler (CPU): interleave block computation and memory statistics
	\ule
\item Common description \ul
	\item Block kernel processor
	\item Full block
	\ule
\item Discussion: wavefront, design similarities, polyhedral theory
\ole
